# R Packages used in these notes {-}

Here, we'll load in some packages used in these notes. The list of R Packages we will use in 432 is more extensive, and is [available on our course website](https://thomaselove.github.io/432/r_packages.html).

```{r load_packages, message = FALSE, warning = FALSE}

library(here)
library(janitor) 
library(magrittr)

library(tableone) 

library(broom) 
library(haven)
library(janitor)
library(patchwork)
library(Hmisc)
library(rms)

library(visdat) 
library(naniar) 
library(caret)
library(simputation)
library(car)
library(mice)
library(leaps)
library(lars)
library(Epi)
library(pROC)
library(ROCR)
library(VGAM)
library(ggridges)
library(pander)
library(arm)
library(survival)
library(survminer)
library(kableExtra)

## and of course, we conclude with...

library(tidymodels)
library(tidyverse) 
```

```{r special_functions}
specify_decimal <- function(x, k) format(round(x, k), nsmall=k)
```

## General Theme for `ggplot` work {-}

```{r}
theme_set(theme_bw())
```


## Data used in these notes {-}

All data sets used in these notes are available on our [Data and Code website](https://github.com/THOMASELOVE/432-data).

Dr. Love is in the process of moving all of the data loads below to their individual chapters.

```{r load_data, message = FALSE, warning = FALSE}
prost <- read_csv("data/prost.csv") 
pollution <- read_csv("data/pollution.csv") 

bonding <- read_csv("data/bonding.csv") 
cortisol <- read_csv("data/cortisol.csv") 
emphysema <- read_csv("data/emphysema.csv") 
resect <- read_csv("data/resect.csv") 
colscr <- read_csv("data/screening.csv") 
colscr2 <- read_csv("data/screening2.csv") 
authorship <- read_csv("data/authorship.csv") 
hem <- read_csv("data/hem.csv") 
leukem <- read_csv("data/leukem.csv") 

```



